Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-23 manuscript.Rmd
Added and merged historical title for The Social Worker. Wrangled new data. Code is functioning.

```{r Figure 1 Small Multiples Supplement}

```{r Figure 2 Journal Growth, eval = TRUE}
#=======================================
# Journals
#=======================================

@@

>>>>

```{r Figure 1 Small Multiples Supplement}
# Create an initial data frame from HD
sm.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N), year = as.numeric(year)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title) %>%
    rename(Year = year, Journal= title)

 abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
 abb$ID <- 1:nrow(abb)
 sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
     select(-X) %>%
     mutate(Documents = ifelse(Documents == 0, NA, Documents))

```{r Figure 2 Journal Growth, eval = FALSE}
#=======================================
# Journals
#=======================================

@@

 sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
 sm.scopus.merged <- group_by(sm.scopus.merged, Journal) %>%
     mutate(Overall.Scopus = sum(Documents, na.rm=TRUE)) %>%
     ungroup()
# 
 # Create labels for the facets
 Overall.N <- distinct(sm.scopus.merged, Abbrev) 
 lab1 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.N), sep=""))
 lab2 <- gsub(" ", "", paste("N=", pretty(Overall.N$Overall.Scopus), sep=""))
 lab <- paste(lab1, lab2, sep="\n")
 xpos = rep(1999, 80)
 ypos = rep(200, 80)

 Overall.N <- distinct(sm.df, Journal)

 ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
     rename(Abbrev = Overall.N.Abbrev)
